HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-17 hermes_paper/hermes_paper.tex
add m4 dataset part

\begin{table*}
  \caption{Results summary on the m4 weekly dataset. For each metric, the average on all our time series is computed. For approaches using neural network, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
  \resizebox{0.85\textwidth}{!}{%
  \begin{tabular}{l||lllll|lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
%    \hline
	 \hline
	 &&&&&&&&&&\\
     \textit{MLP} && 21.349 && - &&& 13.568 && - &&& 3.608 && - &\\
     \textit{RNN} && 15.220 && - &&& 5.132 && - &&& 1.755 && - &\\
     \textit{snaive} && 9.161 && - &&& 2.777 && - &&& 1.000 && - &\\
     \textit{SES} && 9.012 && - &&& 2.685 && - &&& 0.975 && - &\\
     \textit{Theta} && 9.093 && - &&& 2.637 && - &&& 0.971 && - &\\
     \textit{Holt} && 9.708 && - &&& 2.420 && - &&& 0.966 && - &\\
     \textit{Com} && 8.944 && - &&& 2.432 && - &&& 0.926 && - &\\
     \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
     \textit{Uber} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.841 && - &\\
     \textit{\textbf{hermer-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
    %\hline
  \end{tabular}
  }
\label{tab:metricresults}
\end{table*}

@@

>>>>

@@

In addition to the previous results, a HERMES application is also done on the M4 weekly dataset. The M4 dataset gathers 359 weekly time series and shows 3 main differences compare to the fashion dataset. Firstly, sequences have not the same lenght with sequence lenghts lying between 93 and 2610 time steps. Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series show huge contrasting behaviours. Thirldy, compare to the fashion application, the horizon for the M4 competition is set to 13 for the weekly dataset.

\textbf{Training}

The sequence are firstly resized in order to egalize their lenghts. For the shorter ones: the eval and the test set is removed (the last 26 steps). Then the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps. As per time series parametric model training time depends on the sequence lenght, all time series are then croped. At the end, with the addition of the previously removed eval and test set, 300 time steps are kept for each sequence as dataset used to train the HERMES approach.

For this training, The horizon $h$ is set to 13 due to the M4 weekly test set size and the window size $w$ is fixed at 104. For the RNN part, the same architecture than describe in Figure~ \ref{fig:rnn_architecture} is used. The Adam optimizer is used with a learning rate fixed at 0.005 and a batch size set at 8. As the loss function, the same loss than the fashion application is used. As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of example and improve the training. 5 windows are computed for each sequence for the RNN train set. An overview of our train, eval, test set spit and the rolling window is givien in Figure~\ref{}.
The previous parameters: window size, learning rate, batch size and the number of train window per time series are set using a grid search.

\textbf{Benchmarks}

The M4 competion provides a rich collection of benchmarks gatering statistical models and neural network approaches. The same candidates are used in this part as baseline. In addition, the hybrid model named \textit{Uber} of S.Smyl is added to provide a interesting comparison against the HERMES approach. For a complete description and references of the benchmarck models, see \cite{makridakis2020m4}. As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}. Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measure. A complete definition of these metrics is also proposed in \cite{makridakis2020m4}.

\textbf{Results and discussion}

The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}. Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarcks. This results is partially induce by the use of TBATS per-time-series predictors which achieves striking result also on the test set. Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}. With the second application, two importants conclusion can be done. Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks. Secondly, the accuracy gap between the 2 hybrid candidate validate the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.

\begin{table*}
  \caption{Results summary on the m4 weekly dataset. For each metric, the average on all our time series is computed. For approaches using neural network, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
  \resizebox{0.85\textwidth}{!}{%
  \begin{tabular}{l||lllll|lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{SMAPE}} &&& \multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{OWA}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}&&&  \textit{mean}  && \textit{std}& \\
%    \hline
	 \hline
	 &&&&&&&&&&\\
     \textit{MLP} && 21.349 && - &&& 13.568 && - &&& 3.608 && - &\\
     \textit{RNN} && 15.220 && - &&& 5.132 && - &&& 1.755 && - &\\
     \textit{snaive} && 9.161 && - &&& 2.777 && - &&& 1.000 && - &\\
     \textit{SES} && 9.012 && - &&& 2.685 && - &&& 0.975 && - &\\
     \textit{Theta} && 9.093 && - &&& 2.637 && - &&& 0.971 && - &\\
     \textit{Holt} && 9.708 && - &&& 2.420 && - &&& 0.966 && - &\\
     \textit{Com} && 8.944 && - &&& 2.432 && - &&& 0.926 && - &\\
     \textit{Damped} && 8.866 && - &&& 2.404 && - &&& 0.917 && - &\\
     \textit{Uber} && 7.817 && - &&& 2.356 && - &&& 0.851 && - &\\
     \textit{tbats} && 8.111 && - &&& 2.214 && - &&& 0.8 && - &\\
     \textit{\textbf{hermer-tbats}} && \textbf{7.597} && 0.113 &&& \textbf{2.205} && 0.042 &&& \textbf{0.812} && 0.011 &\\
    %\hline
  \end{tabular}
  }
\label{tab:m4metricresults}
\end{table*}
